\thesistitle

### 2019-08-22 sections/results.tex
Separate Metric Results

\section{Refactoring}
%I think the ultimate goal with this thesis is to do experiments with different clone thresholds. Which thresholds give clones that we should refactor? For this, we will measure the maintainability of the refactored source code over different thresholds. These thresholds range from minimum clone size, variability, and gap size.
In our corpus, CloneRefactor has refactored 12.710 clone classes and measured the change in indicated metrics (see Section~\ref{sec:metrics}). Using the presented formulas (see Section~\ref{sec:metricformula}) we determine how the characteristics of the extracted method (see Section~\ref{sec:characteristics}) influence the maintainability of the resulting codebase after refactoring. In this section, we explore the data received by comparing the before- and after snapshots of the system for each separate refactoring.

\subsection{Clone Token Volume}
Figure \ref{fig:duplication} shows the obtained results when plotting the clone size (in tokens) vs the maintainability increase/decrease. On the secondary axis the amount of refactorings that have refactored a clone with the specified amount of tokens is displayed (e.g. the amount of data points the data is based on). As the amount of data points decreases, the datapoints gain less statistical significance.

\begin{figure}[H]
  \includegraphics[width=1\textwidth]{img/duplication}
  \caption{A graph that shows how the size in tokens of the refactored clone affects maintainability. Maintainability on the primary axis and amount of refactorings on the secondary axis.}
  \label{fig:duplication}
\end{figure}

>>>>

\section{Refactoring}
%I think the ultimate goal with this thesis is to do experiments with different clone thresholds. Which thresholds give clones that we should refactor? For this, we will measure the maintainability of the refactored source code over different thresholds. These thresholds range from minimum clone size, variability, and gap size.
In our corpus, CloneRefactor has refactored 12,710 clone classes and measured the change in indicated metrics (see Section~\ref{sec:metrics}). Using the presented formulas (see Section~\ref{sec:metricformula}) we determine how the characteristics of the extracted method (see Section~\ref{sec:characteristics}) influence the maintainability of the resulting codebase after refactoring. In this section, we explore the data received by comparing the before- and after snapshots of the system for each separate refactoring.

\subsection{Clone Token Volume}
Figure \ref{fig:maintainabilityscore} shows the obtained results when plotting the clone volume vs the maintainability increase/decrease. We define the \textit{token volume} as the combined number of tokens in all clone instances in a refactored clone class. The maintainability score, as shown in Figure \ref{fig:maintainabilityscore}, is the average delta maintainability score of all clone classes with the specified token volume that are refactored. As the amount of data points decreases, the datapoints gain less statistical significance, because of which we represent the x-axis as a logaritmic scale. The trendline intersects the ``zero'' line (maintainability does not increase nor decrease) at a token volume of 63.

\begin{figure}[H]
  \includegraphics[width=1\textwidth]{img/maintainabilityscore}
  \caption{The effect of token volume on the delta maintainability score of the refactored system}
  \label{fig:maintainabilityscore}
\end{figure}

The token volume of the clone is equal to the decrease of duplicated tokens, which is part of the maintainability score. Because of that, what we see in Figure~\ref{fig:maintainabilityscore} could largely be caused by this metric. Do determine the effect of clone token volume on each metric, we also plot graphs in which each metric is considered singularly. In Figure~\ref{fig:volume} the average delta volume is shown when clones with the specified token volume are refactored. The trendline intersects the ``zero'' line (average delta volume does not increase nor decrease) at 60 tokens. A higher average delta volume implies a lower maintainability.

\begin{figure}[H]
  \includegraphics[width=1\textwidth]{img/volume}
  \caption{The effect of token volume on the delta volume of the refactored system}
  \label{fig:volume}
\end{figure}

In Figure~\ref{fig:numberofparameters} we show the average delta number of parameters when clones with the specified token volume are refactored. This metric can only increase by the refactoring, because CloneRefactor only applies ``Extract Method'' refactorings that create a method with a certain number of parameters (according to the data needed by the extracted method).

\begin{figure}[H]
  \includegraphics[width=1\textwidth]{img/numberofparameters}
  \caption{The effect of token volume on the number of parameters of the refactored system}
  \label{fig:numberofparameters}
\end{figure}

In Figure~\ref{fig:complexity} we show the average delta complexity when clones with the specified token volume are refactored.

\begin{figure}[H]
  \includegraphics[width=1\textwidth]{img/complexity}
  \caption{The effect of token volume on the complexity of the refactored system}
  \label{fig:complexity}
\end{figure}
